Exploring dimensions of biodiversity in Japanese ferns

### 2021-08-19 ms/manuscript.Rmd
Use APA (6th ed) for citations
as per J. Biogeog. guidance

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::word_document2:
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
    toc: no
    number_sections: no
    reference_docx: template.docx
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
params:
  doc_type: doc
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::word_document2:
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
    toc: no
    number_sections: no
    reference_docx: template.docx
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
params:
  doc_type: doc
editor_options: 
  chunk_output_type: console
---
